---
title: "Midterm"
author: "Melanie Klein"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```

1) Using the if-else coding structure demonstrated in class, write a function that will determine if a number is divisible by 3 and 4  If your number is divisible by 3 and 4, the function generates the following statement: this number is divisible by both 3 and 4. If the function is not divisible by both 3 and 4, the function produces a statement that reads: this number is not divisible by both 3 and 4. Test your function by using the numbers 744 and 159.
```{r}
divisible_3_4 <- function(num) {
  if (num %% 3 == 0 && num %% 4 == 0) {
    return("this number is divisible by both 3 and 4")
  }
  else {
    return("this number is not divisible by both 3 and 4")
  }
}

divisible_3_4(744)
divisible_3_4(159)
```

2) Using r coding methods demonstrated in class, write a function that will produce the difference between the cubes and the squares of the first 5 positive integers. Your output should be given in reverse order. The following number sequence should be produced: 100 48 18 4 0.
```{r}
diff_cube_square <- function(num) {
  difference = num^3 - num^2
  return(rev(difference))
}

diff_cube_square(1:5)
```

3) 
```{r}
U <- c("Maine" , "Texas", "Delaware", "Oregon", "Utah", "Vermont", "Ohio")
```
a. Is U an atomic vector or a list ? U is an atomic vector because all of the objects are of the same data type, character elements. 
b. Using R coding, show two methods for extracting/subsetting the element Utah.
```{r}
U[5]
U[-c(1:4,6:7)]
```
c. Use and show R code that will extract all elements except Ohio.
```{r}
U[-7]
```

4)
```{r}
V = list("Chicago", k = list( 2, 6, 18, 24, 36), FALSE, 13, 1.3, z = 1:20)
```
a. Is V an atomic vector or a list ? Justify your answer. V is a list because the objects are not of the same data type.
b. Use and show R code that will extract the 2nd element of V.
```{r}
V[[2]]
```
c. Use and show R code that classifies the element FALSE as logical.
```{r}
str(V[[3]])
```

5) Copy, paste and run the tribble given below.
```{r}
tribble( ~John, ~Raymond, ~Martha, ~Alice, ~Juan,
         86, 77, 81, 88, 90,
         79, 78, 85, 81, 78,
         76, 75, 88, 94, 81,
         84, 90, 71, 84, 89,
         100, 80, 93, 85, 84,
         90, 73, 70, 88, 93
         ) -> TestScores
TestScores
```
a.	Use and show R code (a map function) to find the mean for each column.
```{r}
map_dbl(TestScores, mean)
```
b.	Use and show R code (a map function) to find the cube of each column element.
```{r}
map_df(TestScores, ~map_dbl(.x, ~(.^3)))
```
c.	Use and show R code (a map function) to convert each column value to 100.
```{r}
map_df(TestScores, ~map_dbl(.x, ~100))
```

6) Use and show R coding that will produce the matrix given below.
```{r}
z <- matrix(nrow = 4, ncol = 4) 
for (m in 1:4) {
  for (n in 1:4) {
    z[m, n] <- (m*n)^2
  }
}
print(z)
```

7)  Use two or three sentences to explain each git command. (Do not run code; you will have that opportunity on the final exam)

a. git clone: Clones a remote repository on your local machine. The entire repository is downloaded so an identical copy of the project can be worked on locally and saved to your computer.

b. git init: Initializes the current local directory into a Git repository. This is used when a project exists locally but doesn't have Git yet.

c. ls: Used to view the contents of a directory. Prints files, folders, and directories in the current directory.

d. git add: Adds the files in your new local repository. This stages it for the first commit so new and changed files are included.

e. touch: Creates an empty file. It can be used as a placeholder file if you don't have data to store at that time.

f. git push -u: Uploads local changes that were committed to a remote repository. -u creates a tracking relationship between the local and remote branches that is saved for future pushes and pulls.

g. git commit -m: Saves the files that you've staged in your local repository. -m lets you write a commit message to describe the changes you made.

h. git branch: Used to create, list, and delete branches. Branches allow multiple people to work on a project at the same time and to work in isolation from the main code.

i. git merge: Merges changes from one branch into another. Modifies the master branch with these changes and resolves any conflicts.