---
title: "Study Guide"
author: "Melanie Klein"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```



# Week 2

## Function
a function is a structured and sequenced set of commands that process input values to produce output values efficiently. A function reduces repetitive calculations that often result in mistakes, errors, and unneeded work.

### Function Structure
function_name <- function (argument/input variables) {
  statements/expression for calculation/equation
  return() or print(paste())
}
function_name(input values)

### Print Output
print(paste()) to print output with string and variable together. paste() converts its arguments to character strings

### Function Example
```{r message=FALSE, warning=FALSE, echo = TRUE, results = 'hide'}
data_frame <- tibble(  
  c1 = rnorm(50, 5, 1.5), 
  c2 = rnorm(50, 5, 1.5),    
  c3 = rnorm(50, 5, 1.5),    
)

data_frame$c1 -> x
x

normalize <- function(x){
  # step 1: create the nominator
  nominator <- x-min(x)
  # step 2: create the denominator
  denominator <- max(x)-min(x)
  # step 3: divide nominator by denominator
  normalize <- nominator/denominator
  # return the value
  return(normalize)
}
normalize(x)
```

## If Else Statement Structure
if (condition) {
  Expr1  (execute expression or command 1)
} else {
  Expr2  (execute expression or command 2)
}

### Multiple Conditions
if
else if
else

### If-Else Function Example
```{r message=FALSE, warning=FALSE, echo = TRUE, results = 'hide'}
check <- function(x) {
  if (x > 0) {
    result <- "Positive"
  }
  else if (x < 0) {
    result <- "Negative"
  }
  else {
    result <- "Zero"
  }
  return(result)
}
```

## For Loop Structure
for (i in vector) {
   Exp	
   }

### Special For Loop Method
```{r message=FALSE, warning=FALSE, echo = TRUE, results = 'hide'}
mtcars 
 
output <- vector("double", ncol(mtcars))   # 1. output
for (i in seq_along(mtcars)) {             # 2. sequence
  output[[i]] <- mean(mtcars[[i]])         # 3. body
}
output
```



# Week 3

## Vector
a collection of "things" or objects. They can be numbers, words, letters, or other miscellaneous items

### Atomic Vectors
the objects are of the same type
homogeneous
six types: logical, integer, double, character, complex, and raw
numeric vectors: integer and double vectors
```{r}
V1 <- c(12, 33, 2, 82, 33)   # integers
V2 <- c(.002, 3.6, 7.32, 4.5, 6.0) # doubles
V3 <- c(FALSE,TRUE,TRUE,FALSE) # logical entries
V4 <- c("JANE", "BILL", "JUAN", "EILEEN", "ANN") # character strings
```

### Lists
the objects can be of different types
heterogeneous
```{r}
L1 <- list(6, 3.8, "every", TRUE)
L2 <- list(TRUE, 12, .0125, "cat", list(2:5))
```

## Type of a Vector
"typeof" function to identify the vector
```{r}
typeof(c(11,15,20.5,37))
typeof(list("ALICE", 2:12, TRUE, 95))
```

## Length of a Vector
"length" to determine the number of elements
```{r}
length(c(11,15,20.5,37))
length(list("ALICE", 2:12, TRUE, 95))
```

## Naming, Describing, or Listing the Content of a Vector
use "set_names" from the purr package
```{r}
set_names(c("Boston","Baltimore","Atlanta", "New York","Cleveland"))
set_names(c(14,12,.003,6,20))
set_names(5:7, c("m", "n", "p"))
```

## Subsetting Vectors
```{r}
X <- c("Boston","Baltimore","Atlanta", "New York","Cleveland")
X[1] # extract the first string
X[c(2,4)] # extract the second and fourth strings
X[c(2,2,2)] # extract the second string three times
X[-4] # drop the fourth string
```

```{r}
U <- c(10, 3, NA, 5, 8, 1, NA)
U[is.na(U)] # extract all missing values
U[!is.na(U)] # extract all values that are not missing
U[U %%2 == 0 & !is.na(U)] # extract all even values
U[U > 2] # extract all values greater than 2 and missing values
U[] # extract all values and missing values
```

## Categorize a List
```{r}
Y <- list("ball", 25, 12.25, FALSE, b = 1:5, c = list(-1, "west"))
str(Y)
```

## Subsetting Lists
use [[]] to subset a single object
```{r}
Y <- list("ball", 25, 12.25, FALSE, b = 1:5, c = list(-1, "west"))
str(Y[[1]])   
str(Y[[4]])   
str(Y[[6]])    
str(Y[['c']])
```

use $ to subset a single object
need to assign a character string to a variable before using $
```{r}
Y <- list("ball", 25, 12.25, FALSE, b = 1:5, c = list(-1, "west"))
Y$b
Y$c
```

### Subsetting to get a list from a list
use str([])
```{r}
Y <- list("ball", 25, 12.25, FALSE, b = 1:5, c = list(-1, "west"))
str(Y[1:3])
str(Y[5:6])
str(Y[ ])
```

## Using the purr package to map functions
calculates values for each column
```{r}
mtcars
map_dbl(mtcars, median)
map_dbl(mtcars, sd)
map_dbl(mtcars, max)
```
round values
```{r}
mtcars
round(map_dbl(mtcars, sd), digits = 1) # round to the nearest tenth
```
piping to apply map functions
```{r}
mtcars
mtcars %>%
  map_dbl(median)
```
modify each value
```{r}
mtcars
mtcars %>% # add 3 to each value
  map(~. + 3)
```

## Practice Problem from Textbook
find a linear model for each type of cylinder categories for vehicles
4, 6, and 8 cylinder vehicles
```{r}
mtcars
# linear model
models <- mtcars %>%
  split(.$cyl) %>%
  map(~lm(mpg ~ wt, data = .))
models
# summary statistics for each model
models %>%
  map(summary)
# find a particular value of the summary, r-squared found two ways
models %>% # method 1
  map(summary) %>% 
  map_dbl(~.$r.squared)
models %>% # method 2
  map(summary) %>% 
  map_dbl("r.squared")
```



# Week 4

## Map Functions map2() and pmap()
these functions make it possible to iterate over multiple arguments simultaneously

### map2()
the function is applied or iterated over two arguments simultaneously 
the two vectors are of the same length
```{r}
x <- list(12, 14, 15, 18, 19)
y <- list(8, 14, 20, 22, 30)

# find the iterative sums
map2(x,y, ~ .x + .y) # method 1, returns individual values
map2_dbl(x,y, ~ .x + .y)  # method 2, returns a list
map2_dbl(x,y,  `+`) # method 3, returns a list
```

```{r}
x <- list(12, 14, 15, 18, 19)
y <- list(8, 14, 20, 22, 30)

# find the summary values
map2_dbl(x,y, min)
map2_dbl(x,y, max)
map2_dbl(x,y, sum)
map2_dbl(x,y, ~.y - .x ) # diff does not work, can also do ~.x - .y
map2_dbl(x,y, mean)
```

74 - 104???

### pmap()
the function is applied or iterated over multiple arguments (more than two) simultaneously
the vectors are of the same length
```{r}
x <- list(12, 14, 15, 18, 19)
y <- list(8, 14, 20, 22, 30)
z <- list(10, 18, 28, 34, 40)

pmap_dbl(list(x,y,z), sum) # find the iterative sums
pmap_dbl(list(x,y,z), min) # find the iterative minimums
pmap_dbl(list(x,y,z), function(first, second, third) (first + second + third)/3) # find the iterative means
```

use iterative code to write descriptions for observations of a data frame
```{r}
tribble( ~Student,  ~Gender, ~Age,
         "John",   "Male",    20,
         "Alice",  "Female",  24,
         "Juan",   "Male",    21,
         "Beth",   "Female",  19,
         "Denise", "Female",  22
         ) -> A

A %>% 
  pmap_chr(~ str_glue("{..1} is a {..2} whose age is {..3}"))
```

using pmap on tribbles
```{r}
tribble( ~mean, ~sd,  ~n,
        5,       1,   15,
        10,      5,   10,
        -3,      10,  20
        ) -> parameters

pmap(parameters, rnorm)
```

## While Loops
```{r}
i <- 1
while (i < 6) {
  print(i)
  i = i+1
}
```

## For Loops
use the break command to end output values
```{r}
x <- 1:11
for (val in x) {
  if (val == 7){
    break
  }
  print(val)
}
```

use the next command to skip over an output value
```{r}
x <- 1:11
for (val in x) {
  if (val == 7){
    next
  }
  print(val)
}
```

loop through data frame columns using the ncol function
```{r}
data <- data.frame(x1 = 10:15,
                   x2 = 66:71,
                   x3 = 14:19)

for(i in 1:ncol(data)) {
    data[ , i] <- data[ , i] + 5 # add 5 to every value
}

data
```

## Nested Loops
a loop within a loop
loop (condition) {
  block of instructions
  loop (condition) {
    block of instructions
  }
}
```{r}
for(i in 1:4) {
  for(j in 1:4) {
    print(i*j)
  }
}
```

### Nested loops to create a matrix
a matrix is a rectangular array of values, characterized by rows and columns
```{r}
matrix1 = matrix(nrow=4, ncol=4) # create a 4 x 4 matrix(4 rows and 4 columns)
for(i in 1:nrow(matrix1)) {        # assigned a variable 'i' for each row
  for(j in 1:ncol(matrix1)) {     # assigned a variable 'j' for each column
    matrix1[i,j] = i*j           # calculating product of two indices
  }
}
print(matrix1)
```

```{r}
z <- matrix(nrow = 3, ncol = 3) 
for (m in 1:3) {
  for (n in 1:3) {
    z[m, n] <- m + n
  }
}
print(z)
```



# Week 5

## Command Line
insert shell script (bash scripting language), hit enter, and the computer executes the command
used to move around in your file system and run git commends
other synonyms are shell, terminal, command line interface, and console
R studio, scroll to Terminal, then go to New Terminal

getwd(): find your working directory in R
pwd [name]: print working directory for the terminal
ls: print files, folders, and directories in the current directory
cd [name]: change the working directory (eg [~/Desktop/FolderA])
touch [name]: creates a new empty file
rm [name]: removes a file
cp [name] [file destination]: makes a copy of a file
mv [current name] [new name]: renames a file
mkdir [name]: creates a directory (eg. mkdir ~/Desktop/Folder2)

## Git
coding and processing
git is a version control system: a progra, that tracks changes to specified files over a period of time and maintains a library of all past versions of those files

## GitHub
posting, showing, hosting
a website that hosts git repositories
a repository is a storage location for data and files
the Git repository tracs all changes made to files in your project, building a history over time

## Git and GitHub
Step 1 Create a new repository on Git hub  (github.com)
Step 2 Open Git Bash
Step 3 Check to make sure that the location of your file matches your working directory
Step 4 Initialize the local directory as a Git repository. enter the code statement   git init
Step 5 git status (Identify the file that you would like to move/push to Github)
Step 6 ls  (you are now looking at specific files that you can push to Github)
Step 7 git add (Add the files in your new local repository. This stages it for the first commit.)
Step 8 Commit the files that you've staged in your local repository. enter the command:  git commit -m "type a message"
Step 9 At the top of your GitHub repository's Quick Setup page, click to copy the remote repository URL. 
Step 10 Enter:  git remote add <some nickname> https://PATOKEN@linkdatafromGithubURL (this will set the new remote)
Step 11 Enter: git remote -v  (this will verify the new remote URL) 
Step 12  Enter:  git push -u <nickname> master (this code will push the file to Github)
Step 13 Go to Github and locate your file
