---
title: "Homework 2"
author: "Melanie Klein"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

Load Packages

```{r message=FALSE}
library(tidyverse) 
library(dplyr)
```

3)  For the following if-else-if coding structure, make an adjustment so that it prints "Team A won"

```{r}
team_A <- 3 # Number of goals scored by Team A
team_B <- 2 # Number of goals scored by Team B

if (team_A > team_B){
  print ("Team A won")
} else if (team_A < team_B){
  print ("Team B won")
} else {
  print ("Team A & B tied")
}
```

4)  Write an if-else if-else sequence of commands that will output the
    following statements and appropriate output; If a value is divisible
    by 3 and 5 the output statement is "divisible by Three and Five", If
    a value is divisible by 3 and 4, the output statement is "divisible
    by Three and Four, If a value is a number that does not fall into
    either category, the output statement should be"neither". Use your
    function to show output statements for values 16, 45, and 24.

```{r}
divisible_345 <- function(num) {
  if (num %% 3 == 0 && num %% 5 == 0) {
    print("divisible by Three and Five")
  } else if (num %% 3 == 0 && num %% 4 == 0) {
    print("divisible by Three and Four")
  } else {
    print("neither")
  }
}

divisible_345(16)
divisible_345(45)
divisible_345(24)
```

5)  Use piping and a dplyr command, show and use R code to produce the
    following modified mpg data table that contains only quantitative
    variables. Now use the "special loop coding chunk", illustrated in
    class, to produce the variance for all variables of the modified
    data table.

```{r}
data(mpg)

mpg_quant <- mpg %>%
  select(displ, cyl, cty, hwy)
mpg_quant

mpg_variance <- vector("double", ncol(mpg_quant))   # 1. output
for (i in seq_along(mpg_quant)) {                   # 2. sequence
  mpg_variance[[i]] <- var(mpg_quant[[i]])          # 3. body
}
mpg_variance
```

6)  Construct a for loop (as illustrated in the notes) that will produce
    the difference between the cube and the square for each prime number
    between 10 and 30. (There are 6 answers. The first answer is 1210,
    your for loop coding should produce the other five answers) 

```{r}
for (i in c(10:30)) {
  prime <- TRUE
  for (x in c(2:(i-1))) {
    if(i %% x == 0) {
      prime <- FALSE
    }
  }
  if (prime) {
    print(i^3 - i^2)
  }
}
```
