---
title: "Klein_Homework9"
author: "Melanie Klein"
date: "`r Sys.Date()`"
output: html_document
---

# Using the mpg data in the ggplot2 package, attempt the following questions using SQL script.
# Suggestion: Explore the data using the techniques learned in the class to
# familiarize yourself with the data. You can also use mpg in the console to
# get a better understanding of what the columns mean.

Load Packages
```{r message=FALSE}
library(tidyverse) 
library(dplyr)
```

1. How many records are in the table?
```{r}

```

2. What are the classes of cars we have in the table?
```{r}

```

3. How many categories of models of cars do we have in the data and what are they?
```{r}

```

4. How many manual(m5) cars do we have in the table?
```{r}

```

5. How many compact cars are made by audi?
```{r}

```

6. How many chevrolet cars are mustang model?
```{r}

```

7. What are the top 2 land rover cars with least engine displacements?
```{r}

```

8. What are the top 15 suv cars that were made in the year 1999 
HINT: suv is a class of car
```{r}

```

9. What are the top 10 cars by highway miles per gallon that are either ford or dodge and are made in 2008
HINT order by highway miles per gallon in descending order to get the top 10
```{r}

```

10. What are the top 10 compact or pickup cars with highway miles per gallon is between 15 and 17, ordered by displ in ascending order and year in descending order
```{r}

```


