---
title: "Homework 4"
author: "Melanie Klein and Lisa Liubovich"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```

1)
a) Use the R function nrow to confirm that the iris data frame has 150 rows. Then use and show R code that features a map function to confirm that the iris data frame has 150 rows.
```{r}
data(iris)
nrow(iris)
map(iris, length)
```

b) Each column of the iris data frame has a unique number of values or objects. For example, the column Sepal.Length has 150 values but 35 of them are unique. Use and show R code that features a map function to find the number of unique values or objects for each column of the iris data frame.
```{r}
map_dbl(iris, n_distinct)
```

2)
Use and show R code that features a nested loop that will produce the 5 by 3 matrix shown below.
```{r}
z <- matrix(nrow = 3, ncol = 5) 
for (m in 1:3) {
  for (n in 1:5) {
    z[m, n] <- n - m
  }
}
print(z)
```

3)
Use and show R code that will produce a tibble that features 10 randomly generated values that are normally distributed, with means of -10, 0, 10 and 100 respectfully.  Run your code again, producing a second tibble, that confirms random values, hence the second table will not have the same values.
```{r}
tribble( ~mean, ~sd,  ~n,
        -10,      1,   10,
          0,      1,   10,
         10,      1,   10,
        100,      1,   10
        ) -> parameters

pmap(parameters, rnorm)
pmap(parameters, rnorm)
```

4) 
```{r}
X <- list(12, 14, 15, 18, 19, 22,10,18,18)
Mean <- list(16, 16, 16, 16, 16,16,16,16,16)
sd <- list(2, 2, 2, 2, 2,2,2,2,2)
```

a) In statistics, a z score indicates the standard deviation distance between the mean and a specific value of the data set. What formula is used to find a z score? Use and show R coding that features a map function to iteratively find z scores across the lists given above.
```{r}
pmap_dbl(list(X,Mean,sd), function(first, second, third) ((first - second) / third)) 
```

b) The test statistic for a population mean is given by the formula ((X - mean)/s/sqrt(n)) Use and show R coding that features a map function to iteratively find test statistics for population means across the lists given above.
```{r}
pmap_dbl(list(X,Mean,sd), function(first, second, third) ((first - second) / third / sqrt(length(X))))
```

5)
```{r}
V = c(10,15,17,22,32,38,42)
```

a) Another purr package function is the keep( ) function. Research, explore, and use the keep( ) function to extract all number from the vector V given above that are less than 20
```{r}
keep(V, V < 20)
```

b) Another purr package function is the discard( ) function. Research, explore, and use the discard( ) function to eliminate all numbers from the vector V given above that are less than 20
```{r}
discard(V, V < 20)
```

6)
Another purr package function is the safely( ) function. Research, explore, and apply the safely( ) function to the given vector below as illustrated.
```{r}
U = list(10,15,"mary",22,32,"james",42)
map(U, safely(~ .x + 15))
```

In four or five sentences, explain the specific output for this problem and how the definition and the application of the safely( ) function is used.

For each object in vector U, the safely() function returns a result and an error. One of these will always be null. For vector U, the objects that are integers return a numeric result and a null error because 15 can be added to them. For vector U, the objects that are character elements return a null result and an error saying that you can't add 15 to a non-numeric argument. 

