---
title: "Klein_Lab4_Week4"
author: "Melanie Klein, Stephen DeFerrari, Spencer Grewe"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE}
library(tidyverse) 
library(dplyr)
```

```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)
```

1) For the lists given above, show and use R code (a map function) to iteratively find the square of the sums across the vectors
```{r}
pmap_dbl(list(x, y, z), function(x, y, z) (x + y + z)**2)
```

```{r}
tribble( ~Student,  ~Gender,    ~Salary,
                   "John",   "Male",       65000,
                   "Alice",  "Female",    73000,
                    "Juan",   "Male",       66000,
                    "Beth",  "Female",    71500,
                    "Denise", "Female",  82000
) -> table
table
```

2) Using the data table above, use and show R code that will output a statement that
is descriptive for all rows of the data table.
The first row is given below.  Your code should produce the other specific statements.
  John who is Male, has a salary that is 65000 dollars per year.
```{r}
table %>%
  pmap_chr(~ str_glue("{..1} who is {..2}, has a salary that is {..3} dollars per year."))
```

3) Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements
are sums of the corresponding columns and rows.
```{r}
z <- matrix( nrow = 5, ncol = 5)
for (m in 1:5) {
  for (n in 1:5) {
    z[m, n] <- m + n
  }
}
print(z)
```

4) Use for loop coding to produce the number sequence shown below:
     Note that the numbers 5 and 10 are missing
1
2
3
4
6
7
8
9
11
12
13
14
15
16
17
18
19
20
```{r}
x <- c(1:20)
for (val in x) {
  if (val == 5 | val == 10) {
    next
  }
  print(val)
}
```



